---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rmeds

<!-- badges: start -->
[![R build status](https://github.com/vcastro/rmeds/workflows/R-CMD-check/badge.svg)](https://github.com/vcastro/rmeds/actions)
<!-- badges: end -->

The goal of rmeds is to map medications from electronic health record (EHR) and 
claims datasets to RXNORM ingredients and to drug classes including
FDA Established Pharmaceutical Classes (EPC), VA drug classes (VA) and Anatomic 
Therapeutic Chemical (ATC) classifications.  

## Installation

You can install the development version of rmeds from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("vcastro/rmeds")
```

## Example

This is a basic example to load the full list of RXNORM ingredients:

```{r example}
library(rmeds)

## load list of ingredients
data("rxnorm_in")
```
